Report

### 2021-07-05 Rmd/report.Rmd
Add contrasts

### Trial-level inclusion criteria

@@

### Participant-level inclusion criteria

@@

>>>>

### Inclusion criteria

#### Trial-level inclusion criteria

@@

#### Participant-level inclusion criteria

@@

### Input variables

* Linear (`ot1`), quadratic (`ot2`), and cubic (`ot3`) orthogonal polynomials of the time domain [@mirman2014growth].
* Language profile (`lp`). Categorical predictor with two levels: *Monolingual* and *Bilingual*. Sum coded as *Monolingual* = -0.5, *Bilingual* = +0.5.
* Trial type (`trial_type1` and `trial_type2`). Categorical predictor with three levels: *Cognate*, *Non-cognate*, and *Unrelated*. We coded two contrasts: `trial_type1`, comparing related trials vs. unrelated trials (*Cognate* + *Non-cognate* vs. *Unrelated*), and `trial_type2`, comparing *Cognate* vs. *Non-cognate* trials. These contrasts were sum-coded (see next table for a summary of the contrast coding) [@schad2018capitalize].

```{r contrasts, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

contrasts(gaze$trial_type) %>% 
  as.data.frame() %>% 
  set_names(paste0("trial_type", 1:2)) %>% 
  rownames_to_column("level") %>% 
  gt(rowname_col = "level")
